slides for lab

### 2023-09-07 04. Analysis/scripts/04-03-reporting-slides.Rmd
Create 04-03-reporting-slides.Rmd
New markdown for reporting slides

```{r include=FALSE}
d <- d %>% 
  mutate(
    .cluster_5 = fct_recode(.cluster_5,
                            "Telecommuters" = "1",
                            "Office visitors" = "2",
                            "Hybrid workers" = "3",
                            "In-office workers" = "4",
                            "Disconnected workers" = "5"),
    .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
  )
```

@@

```{r}
is_alluvia_form(prep_d_05)
```

>>>>

```{r include=FALSE}
d <- d %>% 
  mutate(
    .cluster_5 = fct_recode(.cluster_5,
                            "Telecommuters" = "1",
                            "Office visitors" = "2",
                            "In-office workers" = "3",
                            "Disconnected workers" = "4",
                            "Hybrid workers" = "5"),
    .cluster_5 = fct_relevel(.cluster_5,
                            "Telecommuters",
                            "Office visitors",
                            "Hybrid workers",
                            "In-office workers",
                            "Disconnected workers"
                            ),
    .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
  )
```

```{r}
p_1 <- 
  prep_d_05 %>% 
   mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
  ggplot(aes(y = num, axis1 = position_category_description, axis2 = .cluster_5, fill = .cluster_5)) +
  geom_alluvium(width = 1/12) +
  geom_stratum(width = 1/12,
               # alpha = 1,
               fill = "black",
               color = "white"
               ) +
  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
             fill = "white",
             # , alpha = .05,
              size = 4,
             hjust = "inward"
             ) +
  labs(title = "Linking position categories to work pattern groups") +
  ylab("Number of employees") +
  scale_y_continuous(labels = scales::comma) +
  oescolorrrs::scale_fill_oes() +
  oescolorrrs::scale_color_oes() +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_blank())
```

@@
